Introduction to LLL\\``Cryptography''

### 2021-06-03 paper.tex
Add algorithm LLL and references

\begin{algorithm}[H]
    \vspace*{5px}
    $v_1^* = v1$\;
    \\
    \For{$i \gets 2$ \KwTo $n$}{
        $\mu_{ij} = v_i \cdot v_j^* / \lVert v_j^* \rVert ^ 2$ for $1 \le j < i$ \;
        \\
        $v_i^* = v_i - \sum_{j=1}^{i-1} \mu_{ij}v_j^*$ \;
    }
    \caption{Gram-Schmidt Algorithm}
\end{algorithm}

@@

TODO: Write algorithm and explain some steps

>>>>

\begin{algorithm}[H]
    \vspace*{5px}
    $v_1^* = v1$\;
    \\
    \For{$i \gets 2$ \KwTo $n$}{
        $\mu_{ij} = v_i \cdot v_j^* / \lVert v_j^* \rVert ^ 2$ for $1 \le j < i$ \;
        \\
        $v_i^* = v_i - \sum_{j=1}^{i-1} \mu_{ij}v_j^*$ \;
    }
    \caption{Gram-Schmidt Algorithm}
    \label{alg:gram_schmidt}
\end{algorithm}

@@

\begin{algorithm}[H]
    \vspace*{5px}
    Input basis ${v_1, \ldots, v_n}$ \; \\
    $k = 2$ \; \\
    $v_1* = v_1$ \; \\
    \While{$k \le n$}{
        \For{$j = k -1$ \KwTo $1$ step $-1$} {
            $v_k = v_k - \left\lfloor\mu_{k, j}\right\rceil \boldsymbol{v}_{j}$  [size-reduction] \;
        }
        \eIf{$\lVert v_k^* \rVert^2 \ge (\frac{3}{4} - \mu_{k, k-1}^2) \lVert v_{k-1}^2 \rVert$}{
            $k = k + 1$ \;  [Lovàsz-condition]
        }{
            Swap $v_{k-1}$ and $v_k$ [swap-step] \; \\
            $k = \max(k - 1, 2)$
        }
    }
    Note: At each step, $v_1^*, \ldots, v_k^*$ is the orthogonalized set of vectors
    obtained with the Gram-Schmidt \ref{alg:gram_schmidt}. \\
    \vspace*{5px}
    $\mu_{i,j}$ is the quantity $(v_i \cdots v_j^*) / \lVert v_j^* \rVert^2$. \\
    Output reduced basis ${v_1, \ldots, v_n}$
    \caption{LLL reduction algorithm}
\end{algorithm}

The running time of the algorithm is polynomial and executes the main loop no more than
$\mathcal{O}(n^2\log n + n^2\log M)$ steps, where $M = max \lVert v_i \rVert$. \\

Kelby Ludwig explains an intuition behind every steps of the algorithm \cite{lllintuition}, and Oded Regev
gives a more rigorous explanation of the algorithm and the properties \cite{lllexplanation}.
